---
title       : Pitch for shiny application
subtitle    : Injuries and fatalities in the US by location within a period of time
author      : Alberto Hevia
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
url: 
   assests: ../assets
hittheme: zenburn           #
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Synopsis


Harmful events have caused many injuries and fatalities in the US for the last few years.

The shiny app allows to show the number of injuries and fatalities in a specific location for the entire period of ten years. 

it was managed to use information dataset from The National Oceanic and Atmospheric Administration (NOAA) and filter it to obtain a summary of events in the years between 2000 and 2010.

You can obtain the reference of the dataset and more information in:
http://www.nws.noaa.gov

The purpose of this app is to show graphically the number of fatalities and injuries in a specific location. In addition, the evolution of fatalities and injures is also shown through this period of time.

--- .class #id 

## Criteria / Results

There are several options to show the evolution of fatalities and injuries. 

You can choose between the following criteria:

  * Latitude and Longitude. The values by default are related to Los Angeles.
  * Two dates within you can restrict the period of the evaluation. 
  * The radius in kilometers of the location where you want to evaluate injuries and fatalities. 
  You can find in the following slide more details on how the calculation of the closest locations was implemented.

The results for the above criteria can be displayed as:
  * The graph which shows the total of injuries and fatalities by years and a linear model prediction for them.
  * A summary with the total of injuries and fatalities grouped by years.


--- .class #id

## Distance between two locations

The Earth is not flat, therefore the calculation of distance must consider that the Earth is a circunference.

The following function was used to obtain the distance between two points in the Earth:

```{r code_distance1, echo = TRUE}
distance <- function (p1, p2) {
  # Firstly the latitude and longitude are converted to radians
  pr1 <- c(p1[1]*pi/180, p1[2]*pi/180)
  pr2 <- c(p2[1]*pi/180, p2[2]*pi/180)
  #The absolute distance for latitude and longitude is calculated.
  dx <- abs(pr1[1]-pr2[1])
  dy <- abs(pr1[2]-pr2[2])
  # We apply the formula considering that Earth has some angle and is not flat  
  a <- (sin(dx/2)^2 + cos(pr1[1]))*cos(pr2[1])*sin(dy/2)^2
  c <- 2 * atan(sqrt(a)/sqrt(1-a))
  # The distance is converted to kilometers.
  return = (6371 * c)
}
```

See a sample in the following slide.

--- .class #id

## Overview

The distance between New York (40.70, 74) and Los Angeles (34.05, 118.24) can be calculated as:
```{r code_distance2, echo = TRUE}
p1 <- c(34.05,118.24)
p2 <- c(40.70,74)
print(paste("Kilometers between Los Angeles and New York:",round(distance(p1,p2),2)))
```

    
    
Finally, you can evaluate this shiny app in:

http://alberto-hevia-developing-project.shinyapps.io/Developing

 
  
Thanks

